Twists of supersymmetric gauge theories

### 2020-01-08 paper.tex
started 4d N=2

\begin{proof}
We begin by describing the twist by a holomorphic supercharge $Q_+$, on a Calabi-Yau 4-fold $X_4$.  We can do this by by applying Lemma \ref{CS_to_BF_diml_red_prop} to the minimal twist of 9d super Yang-Mills theory.  More explicitly, the minimal twist of 9d super Yang-Mills theory on $X_4 \times L$ is modelled by mixed Chern-Simons theory on $X_4 \times L_\mr{dR}$. Lemma \ref{CS_to_BF_diml_red_prop} says that if we reduce this mixed Chern-Simons theory in the $L$-direction, we obtain a holomorphic BF theory described by $\map(X_4, T[1]B\gg)$

@@

\begin{proof}
This follows by dimensional reduction of the 8d holomorphic twist of Theorem \ref{8d_holo_twist_thm} and its one-parameter degeneration along one of the directions which is not invariant in the holomorphic theory.  That is, by applying Proposition \ref{CS_to_BF_diml_red_prop} to the family $\map(X_4, B\gg)_{\mr{Hod}}$.
\end{proof}

@@

\begin{proof}
Again, this follows by dimensional reduction from 8 dimensions, this time from the intermediate twist of Theorem \ref{8d_rank2_twist_thm}, again by an application of Proposition \ref{CS_to_BF_diml_red_prop}.
\end{proof}

@@

\begin{proof}
We obtain this description by starting with the 1-parameter family of twisted theories from Theorem \ref{7d_holo_twist_thm}, and dimensionally reducing along one of the Calabi-Yau directions.  That is, by applying Proposition \ref{CS_to_BF_diml_red_prop} to the family of twists in 7-dimensions.
\end{proof}

@@

\begin{proof}
We now start with the twisted theory from Theorem \ref{7d_rank2_twist_thm}, with 5 invariant directions, and we dimensionally reduce in an de Rham direction.  That is, we apply Proposition \ref{CS_diml_red_prop}.
\end{proof}

@@

\begin{proof}
As we have done in higher dimensions, we start with with the 1-parameter family of twisted theories from Theorem \ref{6d_holo_twist_thm}, and dimensionally reduce along one of the Calabi-Yau directions by applying Proposition \ref{CS_to_BF_diml_red_prop} to the family of twists in 6-dimensions.
\end{proof}

@@

\begin{proof}
We now take the twist of 6d $\mc N=(1,1)$ super Yang-Mills with 5 invariant directions, as calculated in Theorem \ref{6d_rk22_twist_thm}, and dimensionally reduce in the unique non-invariant direction.  That is, we apply Proposition \ref{CS_to_BF_diml_red_prop} to the flat curve $C$ to obtain the required topological theory.
\end{proof}

@@

\begin{prop}[See also \cite{SWchar}]
The minimal twist of 4d $\cN=1$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=1$ chiral multiplet valued in a representation $R$ is equivalent to holomorphic $BF$ theory for the Lie algebra $\fg$ coupled to the holomorphic $\beta\gamma$ system with values in the representation $R$. 
\end{prop}

@@

>>>>

\begin{proof}
We begin by describing the twist by a holomorphic supercharge $Q_+$, on a Calabi-Yau 4-fold $X_4$.  We can do this by by applying Proposition \ref{CS_to_BF_diml_red_prop} to the minimal twist of 9d super Yang-Mills theory.  More explicitly, the minimal twist of 9d super Yang-Mills theory on $X_4 \times L$ is modelled by mixed Chern-Simons theory on $X_4 \times L_\mr{dR}$. Proposition \ref{CS_to_BF_diml_red_prop} says that if we reduce this mixed Chern-Simons theory in the $L$-direction, we obtain a holomorphic BF theory described by $\map(X_4, T[1]B\gg)$

@@

\begin{proof}
This follows by dimensional reduction of the 8d holomorphic twist of Theorem \ref{8d_holo_twist_thm} and its one-parameter degeneration along one of the directions which is not invariant in the holomorphic theory.  That is, by applying Proposition \ref{CS_diml_red_prop} to the family $\map(X_4, B\gg)_{\mr{Hod}}$.
\end{proof}

@@

\begin{proof}
Again, this follows by dimensional reduction from 8 dimensions, this time from the intermediate twist of Theorem \ref{8d_rank2_twist_thm}, again by an application of Proposition \ref{CS_diml_red_prop}.
\end{proof}

@@

\begin{proof}
We obtain this description by starting with the 1-parameter family of twisted theories from Theorem \ref{7d_holo_twist_thm}, and dimensionally reducing along one of the Calabi-Yau directions.  That is, by applying Proposition \ref{CS__diml_red_prop} to the family of twists in 7-dimensions.
\end{proof}

@@

\begin{proof}
We now start with the twisted theory from Theorem \ref{7d_rank2_twist_thm}, with 5 invariant directions, and we dimensionally reduce in an de Rham direction.  That is, we apply Proposition \ref{CS_to_BF_diml_red_prop}.
\end{proof}

@@

\begin{proof}
As we have done in higher dimensions, we start with with the 1-parameter family of twisted theories from Theorem \ref{6d_holo_twist_thm}, and dimensionally reduce along one of the Calabi-Yau directions by applying Proposition \ref{CS_diml_red_prop} to the family of twists in 6-dimensions.
\end{proof}

@@

\begin{proof}
We now take the twist of 6d $\mc N=(1,1)$ super Yang-Mills with 5 invariant directions, as calculated in Theorem \ref{6d_rk22_twist_thm}, and dimensionally reduce in the unique non-invariant direction.  That is, we apply Proposition \ref{CS_diml_red_prop} to the flat curve $C$ to obtain the required topological theory.
\end{proof}

@@

\begin{thm}[See also \cite{SWchar}]
The minimal twist of 4d $\cN=1$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=1$ chiral multiplet valued in a representation $R$ is equivalent to holomorphic $BF$ theory for the Lie algebra $\fg$ coupled to the holomorphic $\beta\gamma$ system with values in the representation $R$. 
\end{thm}

@@

\vspace{-10pt}
\paragraph{Twisting data:}
There are three classes of square-zero supercharge in the 3d $\mc N=2$ supersymmetry algebra, distinguished by the ranks of the two summands $(Q_+,Q_-) \in S_+ \otimes W \oplus S_- \otimes W^*$.
\begin{itemize}
 \item Rank $(1,0)$ and $(0,1)$ supercharges automatically square to zero.  The corresponding twists are holomorphic, and coincide with the 4d $\mc N=1$ twists discussed above.
 \item Rank $(2,0)$ and $(0,2)$ supercharges also automatically square to zero. The corresponding twists are topological (the \emph{Donaldson twist}).
 \item Rank $(1,1)$ square-zero supercharges have three invariant directions.
\end{itemize}

We will identify the latter two twists as further deformations of the minimal twist, which we can describe similarly to what we saw for $\mc N=1$.

\begin{theorem} \label{4d_2_holo_twist_thm}
The minimal twist of 4d $\mc N=2$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ on a Calabi-Yau surface $S$ is perturbatively equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $\mr{Map}(S, T^*[1](U/\!/\gg))$.
\end{theorem}

\begin{proof}
To show this, we start with the 5d $\mc N=1$ minimal twist from Theorem \ref{5d_holo_twist_theorem} and dimensionally reduce in the de Rham direction $L_{\mr{dR}}$.  That is, we apply Proposition \ref{CS_to_BF_diml_red_prop} to the theorem obtained in Theorem \ref{5d_holo_twist_theorem}.
\end{proof}
